manuscript_one

### 2024-01-26 manuscript_one.Rmd
updating formatting for table

library(tidyverse)
library(janitor)
library(RColorBrewer)
library(caret)
library(ggpubr)
library(MASS)
library(lme4)
library(kableExtra)
library(rcompanion)
library(magrittr)
library(magick)
library(patchwork)
library(kableExtra)
library(webshot2)
source("my_functions.R")
setup_libs()

@@

#create a dataframe with the table_one data 
table_one_df = data.frame(
  "Species" = c(rep("C. anthonyi", 2), rep("C. productus", 2), rep("C. anntenarius", 2)), 
  "Sex" = c("Females", "Males", "Females", "Males", "Females", "Males"),
  "Prevalence Infested" = c("100% <br> (n = 52)", "83% <br> (n = 12)", "86% <br> (n = 7)", "80% <br> (n = 5)", "100%  <br> (n = 3)", "100% <br> (n = 7)"),
  "Prevalence with Adults in Egg Mass"= c("100% <br> (n = 52)", NA, "100% <br>(n = 3)", NA, "100% <br>(n = 3)", NA),
  "Mean Density of Nicothoid Eggs in Host Eggs" = c("1570.6 ± 2411.3 <br> (n = 27)", NA, NA, NA, NA, NA),
  "Mean Density of Larvae in Host Eggs" = c("*282.2 ± 440.7 <br> (n = 27)", NA, NA, NA, NA, NA),
  "Mean Density of Adults in Host Eggs" = c("*3.8 ± 6.3 <br> (n = 41)", NA, NA, NA, NA, NA),
  "Mean Density of Larvae in Gills" = c("14966 ± 22175 <br> (n = 18)", "235 ± 373 <br> (n = 10)", "24 ± 32 <br> (n = 3)", "63 ± 64 <br> (n = 4)", "5120 ± 5741 <br> (n = 3)", "60 ± 40 <br> (n = 5)"))

@@

### i) Adults
```{r}
#plot the number of adults over time per 1000 host eggs
adult_timeseries <- ggplot() +
  geom_point(data = adult_all_new,
            aes(x = day, y = scaled_adults), color = publication, size = 0.75) +
  geom_line(data = adult_all_avg_new_day,
            aes(x = day, y = scaled_adults)) +
  theme_classic() +
  labs(y = "Adult Nicothoids per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(adult_all_new$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 5, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### ii) Larvae
```{r}
#plot the number of juvniles over time per one million host eggs
larvae_timeseries <- ggplot() +
  geom_point(data = total_df,
            aes(x = day, y = scaled_juveniles), color = publication, size = 0.75) +
  geom_line(data = total_df_avg,
            aes(x = day, y = scaled_juveniles)) +
  theme_classic() +
  labs(y = "Larval Nicothoids per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(total_df$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 5, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iii) Total Nicos
```{r}
#plot the number of juvniles over time per one million host eggs
total_nicos_timeseries <- ggplot() +
  geom_point(data = total_df,
            aes(x = day, y = scaled_total_nicos), color = publication, size = 0.75) +
  geom_line(data = total_df_avg,
            aes(x = day, y = scaled_total_nicos)) +
  theme_classic() +
  labs(y = "Total Nicothoids per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(total_df$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 5, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iv) Nico Eggs
```{r}
#plot the number of nico eggs over time per one million host eggs
nico_egg_timeseries <- ggplot() +
  geom_point(data = nico_egg_df,
            aes(x = day, y = scaled_nico_eggs), color = publication, size = 0.75) +
  geom_line(data = nico_egg_df_avg,
            aes(x = day, y = scaled_nico_eggs)) +
  theme_classic() +
  labs(y = "Nicothoid Eggs per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(nico_egg_df$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 5, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

## B) Table
```{r}
#assign column names for table one
colnames(table_one_df) <- c("Species", "Sex", "Prevalence Infested", "Prevalence with Adults <br> in Egg Mass", "Mean Density of Nicothoid <br> Eggs in Host Eggs", "Mean Density of <br> Larvae in Host Eggs", "Mean Density of Adults <br> in Host Eggs", "Mean Density of <br> Larvae in Gills")

#create the table 
final_table_one <- table_one_df %>%
  kable(html_font = "Times New Roman", 
      digits = 0,
      align = "c",
      booktabs = T, 
      escape = F) %>%
  kable_styling(latex_options = c("striped","hold_position", html_font = "Times New Roman", full_width = F, font_size = 10)) %>%
  column_spec(1, italic = T, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(2, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(4, extra_css = "border-bottom: 1px solid;") %>%
  collapse_rows(columns = 1, valign = "middle") %>%
  column_spec(2, italic = F) %>%
  kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
  save_kable(file = "figures/final_table_one.png", 
             zoom = 3)

>>>>

library(RColorBrewer)
library(caret)
library(ggpubr)
library(rcompanion)
library(magrittr)
library(magick)
library(patchwork)
library(kableExtra)
library(webshot2)
library(devtools)
source("my_functions.R")
setup_libs()

@@

#create a dataframe with the table_one data 
table_one = data.frame(
  "Species" = c(rep("C. anthonyi", 2), rep("C. productus", 2), rep("C. anntenarius", 2)), 
  "Sex" = c("Females", "Males", "Females", "Males", "Females", "Males"),
  "Prevalence Infested" = c("100% <br> (n = 52)", "83% <br> (n = 12)", "86% <br> (n = 7)", "80% <br> (n = 5)", "100%  <br> (n = 3)", "100% <br> (n = 7)"),
  "Prevalence with Adults in Egg Mass"= c("100% <br> (n = 52)", NA, "100% <br>(n = 3)", NA, "100% <br>(n = 3)", NA),
  "Mean Density of Nicothoid Eggs in Host Eggs" = c("1570.6 ± 2411.3 <br> (n = 27)", NA, NA, NA, NA, NA),
  "Mean Density of Larvae in Host Eggs" = c("*282.2 ± 440.7 <br> (n = 27)", NA, NA, NA, NA, NA),
  "Mean Density of Adults in Host Eggs" = c("*3.8 ± 6.3 <br> (n = 41)", NA, NA, NA, NA, NA),
  "Mean Density of Larvae in Gills" = c("14966 ± 22175 <br> (n = 18)", "235 ± 373 <br> (n = 10)", "24 ± 32 <br> (n = 3)", "63 ± 64 <br> (n = 4)", "5120 ± 5741 <br> (n = 3)", "60 ± 40 <br> (n = 5)"))

@@

### i) Adults
```{r}
#plot the number of adults over time per 1000 host eggs
adult_timeseries <- ggplot() +
  geom_point(data = adult_all_new,
            aes(x = day, y = scaled_adults), color = publication, size = 0.75) +
  geom_line(data = adult_all_avg_new_day,
            aes(x = day, y = scaled_adults)) +
  theme_classic() +
  labs(y = "Adult Nicothoids per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(adult_all_new$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### ii) Larvae
```{r}
#plot the number of juvniles over time per one million host eggs
larvae_timeseries <- ggplot() +
  geom_point(data = total_df,
            aes(x = day, y = scaled_juveniles), color = publication, size = 0.75) +
  geom_line(data = total_df_avg,
            aes(x = day, y = scaled_juveniles)) +
  theme_classic() +
  labs(y = "Larval Nicothoids per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(total_df$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iii) Total Nicos
```{r}
#plot the number of juvniles over time per one million host eggs
total_nicos_timeseries <- ggplot() +
  geom_point(data = total_df,
            aes(x = day, y = scaled_total_nicos), color = publication, size = 0.75) +
  geom_line(data = total_df_avg,
            aes(x = day, y = scaled_total_nicos)) +
  theme_classic() +
  labs(y = "Total Nicothoids per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(total_df$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iv) Nico Eggs
```{r}
#plot the number of nico eggs over time per one million host eggs
nico_egg_timeseries <- ggplot() +
  geom_point(data = nico_egg_df,
            aes(x = day, y = scaled_nico_eggs), color = publication, size = 0.75) +
  geom_line(data = nico_egg_df_avg,
            aes(x = day, y = scaled_nico_eggs)) +
  theme_classic() +
  labs(y = "Nicothoid Eggs per One Million Crab Eggs") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(nico_egg_df$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

## B) Table
```{r}
#assign column names for table one
colnames(table_one) <- c("Species", "Sex", "Prevalence Infested", "Prevalence with Adults <br> in Egg Mass", "Mean Density of Nicothoid <br> Eggs in Host Eggs", "Mean Density of <br> Larvae in Host Eggs", "Mean Density of Adults <br> in Host Eggs", "Mean Density of <br> Larvae in Gills")

#create the table 
final_table_one <- table_one %>%
  kable(format = "html",
        html_font = "Times New Roman",
        digits = 0,
        align = "c",
        booktabs = T, 
        escape = F) %>%
  kable_styling(bootstrap_options = c("striped","hold_position")) %>%
  column_spec(1, italic = T, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(2, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(4, extra_css = "border-bottom: 1px solid;") %>%
  collapse_rows(columns = 1, valign = "middle") %>%
  kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
  save_kable(file = "figures/final_table_one.png",
             zoom = 3)
